Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-06-15 paper/ms.tex
re-structure

When we include the tightest constraints on the mock catalogs, we find
that there are 30 set of parameters of our model, out of the original
90000 initial models, that are consistent with the observational
constraints at redshift $3.1$: the distribution of the number density,
the inferred values for the average occupation fraction. The
consistency with the angular correlation, in terms of the $\chi^2$
statistics did not help to discard any additional models with a
significant degree of confidence.

These 30 models can be classified into two families of the same
size. The first, where the range $M_{\rm min}-M_{\rm max}$ is narrow,
typically of less than $<1.0$ dex. While in the second familiy the
extent $>1.0$ dex. In the first case the minimum halo mass is found to
be in a wide range $10^{10}\hMsun <M_{\rm min}< 10^{11.5}\hMsun$ while
in the second case, only models with $M_{\rm min}\sim 10^{10.9}\hMsun$
are compatible with the observational contraints. In what follows we
discuss the implications of the existence of these two families of
models.

@@

Observations by  \cite{Hayes2010} constrained the occupation fraction of $f_{\rm 
  occ}$ at $z=2.2$ to be $f_{\rm occ}=0.10$. This estimation was based
on blind surveys of the H$\alpha$ and Lyman $\alpha$ line with the
European Southern 
Observatorio (ESO) Very Large Telescope (VLT). Using corrections by
extinction to obtain an estimate for the intrinsic H$\alpha$
luminosity, and using values for the theoretical expectation of the
ratio Lyman$\alpha$/H$\alpha$ they derive an bulk escape fraction for
the Lyman$\alpha$ radiation of $f_{\rm esc}=(5.3\pm 3.8)\%$ or $f_{\rm
esc}=(10.7\pm 2.8)\%$ if a different dust correction is used. The
authors show that the luminosity function for LAEs at $z=2.2$ is
consistent with the escape fraction being constant for every galaxy
regardless of its luminosity. From this results they derive that
almost $90\%$ of the star forming galaxies emit insufficient
Lyman $\alpha$ to be detected, effectively setting the occupation
fraction to be $f_{\rm occ}=0.10$. For the cosmological parameters
used in this \documentname the age of the universe between $z=3.1$ and
$z=2.2$ has changed by $\sim 1$ Gyr. We assume that the physical
conditions that determine the escape fraction $f_{\rm esc}$ and the
occupation fraction $f_{\rm  occ}$ remain similar over that time
scale.

>>>>

Considering the tightest constraints on the mock catalogs 
with the angular correlation function and the maximal
number of consistent mock surveys we end up with 50 models out of the
original 90000 models.

We find that most of the models with an occupation fraction $f_{\rm
  occ}\leq 0.2$ are those with mean correlation lenghts within the
observational uncertainty. Most of the models with $f_{\rm occ}$ are
those that are consistent only when the statistical uncertainty from
the mock cosmic variance is taken into account.

This slight preference towards low occupations fractions is remarkably
close to  the observational constraint $f_{\rm occ}$ derived at
$z=2.2$ by \cite{Hayes2010}.  This estimation was based
on blind surveys of the H$\alpha$ and Lyman $\alpha$ line with the
European Southern  Observatorio (ESO) Very Large Telescope
(VLT). Using corrections by extinction to obtain an estimate for the
intrinsic H$\alpha$ luminosity, and using values for the theoretical
expectation of the ratio Lyman$\alpha$/H$\alpha$ they derive an bulk escape fraction for
the Lyman$\alpha$ radiation of $f_{\rm esc}=(5.3\pm 3.8)\%$ or $f_{\rm
esc}=(10.7\pm 2.8)\%$ if a different dust correction is used. The
authors show that the luminosity function for LAEs at $z=2.2$ is
consistent with the escape fraction being constant for every galaxy
regardless of its luminosity. From this results they derive that
almost $90\%$ of the star forming galaxies emit insufficient
Lyman $\alpha$ to be detected, effectively setting the occupation
fraction to be $f_{\rm occ}=0.10$. For the cosmological parameters
used in this \documentname the age of the universe between $z=3.1$ and
$z=2.2$ has changed by $\sim 1$ Gyr. We assume that the physical
conditions that determine the escape fraction $f_{\rm esc}$ and the
occupation fraction $f_{\rm  occ}$ remain similar over that time
scale.

%that there are 60 set of parameters of our model, out of the original
%90000 initial models, that are consistent with the observational
%constraints at redshift $3.1$: the distribution of the number density,
%the inferred values for the average occupation fraction. The
%consistency with the angular correlation, in terms of the $\chi^2$
%statistics did not help to discard any additional models with a
%significant degree of confidence.

These 50 models can be classified into two families of the same
size. The first, where the range $M_{\rm min}-M_{\rm max}$ is narrow,
typically of less than $<1.0$ dex. While in the second familiy the
extent $>1.0$ dex. In the first case the minimum halo mass is found to
be in a wide range $10^{10}\hMsun <M_{\rm min}< 10^{11.5}\hMsun$ while
in the second case, only models with $M_{\rm min}\sim 10^{10.9}\hMsun$
are compatible with the observational contraints. In what follows we
discuss the implications of the existence of these two families of
models.

@@
